### 2022-05-31 doc/VerticalArrangements.tex
fixed issue with how compareplot was being outputted. Minor edits to intro and conclusion.

We then provide a case study (in progress) from an industry, solid waste management, that has seen a large number of mergers with both horizontal and vertical elements.  Broadly speaking, the supply chain of this sector involves haulers at the downstream level that bring trash to disposal facilities at the upstream level.  A variety of firms participate in these services, with some owning their own hauling and disposal assets, while others are active in only a segment of the market.

@@

This paper relaxes an assumption made in \citeN{ST2021}: that mergers occur in vertical supply chains where in the pre-merger state, no firms are vertically integrated. Relaxing this constraint is important as competition authorities are routinely called upon to investigate mergers where either the merging parties or a third party are already vertically integrated. Here, we show using numerical simulations that relaxing these assumptions can result in merger outcomes that are markedly different from those when these assumptions are maintained. We intend to use two recent trash mergers to investigate the importance of these assumptions in predicting merger harm. Our hope is that future research will focus on some of the other assumptions made in \citeN{ST2021}, such as how the presence of siloed firms, two-part tariffs, or large fixed costs affect the Nash bargaining game and therefore merger outcomes.

>>>>

We then employ this model to investigate the 2021 merger of two solid waste management firms, Republic and Santek, in one geographic market: Chattanooga, Tennessee. The solid waste management industry has seen a large number of mergers with both horizontal and vertical elements.  Broadly speaking, the supply chain of this sector involves haulers at the downstream level that bring trash to disposal facilities at the upstream level.  A variety of firms participate in these services, with some owning their own hauling and disposal assets, while others are active in only a segment of the market. We find that ignoring vertical integration substantially understates harm to consumers in Chattanooga.

@@

This paper relaxes an assumption made in \citeN{ST2021}: that mergers occur in vertical supply chains where in the pre-merger state, no firms are vertically integrated. Relaxing this constraint is important as competition authorities are routinely called upon to investigate mergers where either the merging parties or a third party are already vertically integrated. Here, we show using numerical simulations that relaxing these assumptions can result in merger outcomes that are markedly different from those when these assumptions are maintained.  This is further illustrated by the results from our simulations in the Republic/Santek merger, where we find that ignoring existing vertical relationships drastically understates harm to Chattanooga consumers. Our hope is that future research will focus on some of the other assumptions made in \citeN{ST2021}, such as how the presence of siloed firms, two-part tariffs, or large fixed costs affect the Nash bargaining game and therefore merger outcomes.
